Parameter estimation

### 2023-06-27 SFE-article/Sections/Results.tex
27.06

	The further spifflication of the process model can be introduced based on $C_{lim}$ results. Values of saturation concentrations are at the level of 1e5 which is an internal upper bound of the optimizer used if $+\infty$ indicates the upper bound. This suggest that solvent hasn't reach the saturation concentration and the process model can be simplified by replacing $\gamma(c_f)$ function with unity.

>>>>

	The $\Upsilon$ coefficient
